---
title: "Untitled"
author: "Yixin Ren"
date: "12/15/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set working directory, load the data, source the function script
```{r}
stwed ("")
source("project function.R")
load("ebaydata.RData")
```

## Prepare the data
```{r}
## Create new variable "time of year"
summary(ebaydatafinal$startingdate)
firstdate = which(ebaydatafinal$startingdate ==16844)
firstdate = ebaydatafinal[firstdate, ]
firstdate$startdate[1]
ebaydatafinal$timeofyear[ebaydatafinal$startingdate-16844<=244] <- "Autumn"
ebaydatafinal$timeofyear[ebaydatafinal$startingdate-16844<=200] <- "Summer"
ebaydatafinal$timeofyear[ebaydatafinal$startingdate-16844<=108] <- "Spring"
ebaydatafinal$timeofyear[ebaydatafinal$startingdate-16844<=16] <- "Winter"

##################################################################
## Group the production year variable
ebaydatafinal$yeargroup = ebaydatafinal$year
ebaydatafinal$yeargroup[ebaydatafinal$year < 2000] <- "6"
ebaydatafinal$yeargroup[ebaydatafinal$year < 1990] <- "5"
ebaydatafinal$yeargroup[ebaydatafinal$year < 1980] <- "4"
ebaydatafinal$yeargroup[ebaydatafinal$year < 1970] <- "3"
ebaydatafinal$yeargroup[ebaydatafinal$year < 1960] <- "2"
ebaydatafinal$yeargroup[ebaydatafinal$year < 1950] <- "1"

##################################################################
## Group the car model
ebaydatafinal$modelgroup = "smallvehicle"
ebaydatafinal$modelgroup[ebaydatafinal$model<=36 & ebaydatafinal$model>=33] <- "trunk"
ebaydatafinal$modelgroup[ebaydatafinal$model<=42 & ebaydatafinal$model>=40] <- "trunk"

##################################################################
## Select variables that may affect revenue, drop observations with missing values, turn catagorical variables into "charactor" format
ebaydatafinal$carmodelgroup = paste(ebaydatafinal$maker, ebaydatafinal$modelgroup)
newdata = ebaydatafinal[c("biddy1", "numbids", "timeofyear", "buyitnow", "text", "photos", "length", "carmodelgroup","miles", "yeargroup", "ding", "dent", "scratch", "problem", "rust", "condition")]
newdata = newdata[!is.na(newdata$biddy1),]
newdata = newdata[!is.na(newdata$yeargroup),]
newdata = newdata[!is.na(newdata$photos),]
newdata = newdata[-which(newdata$photos==-1),]
newdata$timeofyear=as.character(newdata$timeofyear)
newdata$carmodelgroup=as.character(newdata$carmodelgroup)
newdata$yeargroup=as.character(newdata$yeargroup)
newdata$condition=as.character(newdata$condition)
```


##Summary and describe the main variables
```{r}
## Decribe number of bidders
sum(newdata$numbids>100)
sum(newdata$numbids>400)
newdata2 = newdata[-which(newdata$numbids>100),]
hist(newdata2$numbids, main="Number of Bidders", xlab="Number of Bidders", col = "gray")
summary(newdata2$numbids)

########################################################################
## Decribe revenue
sum(newdata$biddy1>80000)
newdata2 = newdata[-which(newdata$biddy1>80000),]
hist(newdata2$biddy1, main="Revenue", xlab="Revenue", col = "gray")
summary(newdata2$biddy1)
```


## Use Cross-Validation on linear model to do variable selection
```{r}
predict.regsubsets = function (object ,newdata ,id ,...){
form=as.formula (object$call [[2]])
mat=model.matrix (form ,newdata )
coefi =coef(object ,id=id)
xvars =names (coefi )
mat[,xvars ]%*% coefi
}

require("leaps")
k = 10
s = 32
set.seed (1)
folds = sample (1:k,nrow(newdata),replace =TRUE)
cv.errors = matrix (NA,k,s,dimnames = list(NULL , paste (1:s)))
for(j in 1:k){
best.fit = regsubsets(biddy1~.,data = newdata[folds!=j,], nvmax = s, method = "forward")
for(i in 1:s) {
pred = predict(best.fit,newdata[folds ==j,],id=i)
cv.errors[j,i]=mean((newdata$biddy1[folds ==j]-pred)^2)
}
}
mean.cv.errors =apply(cv.errors, 2, mean)
par(mfrow =c(1,1))
plot(mean.cv.errors ,type='b')

###############################################################
## Choose a new set of variables based on the CV result
ebaydatafinal2 = ebaydatafinal[!is.na(ebaydatafinal$bookvalue),]
newdata = ebaydatafinal2[c("biddy1", "numbids", "timeofyear", "buyitnow", "text", "photos", "length", "bookvalue","miles","condition")]
newdata = newdata[!is.na(newdata$biddy1),]
newdata = newdata[!is.na(newdata$photos),]
newdata = newdata[-which(newdata$photos==-1),]
newdata$timeofyear=as.character(newdata$timeofyear)
newdata$condition=as.character(newdata$condition)
library(caret)
dmy <- dummyVars(" ~ .", data = newdata)
newdata2 <- data.frame(predict(dmy, newdata = newdata))
```


## Model selection (parametric models: Lasso, Ridge, and Neural Network)
## Lasso and Ridge
```{r}
library(glmnet)
for (per in c(.5,.9)) {
  #test group
  set.seed(0)
  test_ind = generate_indices(nrow(newdata), per)
  
  ##########################################################
  #linear model
  linear_mse = linear_model(newdata,test_ind); #linear_mse
  print(paste("linear_mse is ",linear_mse))
  ##########################################################
  #covariate selection
  cs_mse = covariate_selection(newdata2,test_ind); #cs_mse
  print(paste("covariate_shrink_mse is ",cs_mse))
  ##########################################################
  #Lasso and Ridge lambda selection through cv
  ridge_lambda = optimize(cv,interval=c(0,10),newdata2=newdata2,test_indices=test_ind,ridge=T)$minimum
  lasso_lambda = optimize(cv,interval=c(0,1),newdata2=newdata2,test_indices=test_ind,ridge=F)$minimum
  ##########################################################
  #Lasso and Ridge
  ridge_mse = ridge_lasso(newdata2,test_ind=test_ind,lambda=ridge_lambda,ridge=T); #ridge_mse
  lasso_mse = ridge_lasso(newdata2,test_ind=test_ind,lambda=lasso_lambda,ridge=F); #lasso_mse
  print(paste("ridge_mse is ",ridge_mse))
  print(paste("lasso_mse is ",lasso_mse))
}

##########################################################
 ##See if ridge dropped any covariate, predict winning bid 
y = newdata2$biddy1
covariates = newdata2[,2:ncol(newdata2)]
ridge.fit = glmnet(as.matrix(covariates[-test_ind,]),y[-test_ind],alpha=0,lambda=ridge_lambda)
coef(ridge.fit)
ridge.pred = predict(ridge.fit,as.matrix(covariates[test_ind,]),s=ridge_lambda) 

#######################################################
## Compute the siginificance level of the ridge regression coefficients
library(ridge)
ridgereg <- linearRidge(biddy1~numbids+timeofyear+buyitnow+text+
                      photos+length+bookvalue+miles+condition,newdata)
summary(ridgereg) 
```

## Neural Network
```{r}
require(h2o)
h2o_inst = h2o.init(nthreads=-1,
                    min_mem_size = '5G',
                    max_mem_size = '10G')

test_ind = sample.int(nrow(newdata2),round(nrow(newdata2)*.2))

train = newdata2[-test_ind,]
test = newdata2[test_ind,]

h2o.train = as.h2o(train)
h2o.test = as.h2o(test)

neural_net = h2o.deeplearning(
  x = 2:ncol(train),
  y=1,
  training_frame = h2o.train,
  validation_frame = h2o.test,
  hidden=c(64,32,16),
  epochs=200
  
)

nn_mse = h2o.mse(neural_net,valid=T)
nn_mse/1e6

fitted_values = as.data.frame(h2o.predict(neural_net,h2o.train))$predict

View(cbind(train$biddy1,fitted_values))
plot(fitted_values,train$biddy1,xlim=c(0,1e5),
     ylim=c(0,1e5))
plot(function(x)x,add=T,xlim=c(0,1e7))
```


## Model selection (non-parametric models: random forest)
```{r}
random_forest = h2o.randomForest(
  x = 2:ncol(train),
  y=1,
  training_frame = h2o.train,
  validation_frame = h2o.test,
  ntrees=500
  
)

rf_mse = h2o.mse(random_forest,valid=T)
rf_mse/1e6
```


###############################################################################


## The most commonly observed car model in the data
```{r}
ebaydatafinal$carmodel = paste(ebaydatafinal$maker, ebaydatafinal$model)
newdata3 = ebaydatafinal[c("biddy1", "numbids", "timeofyear", "buyitnow", "text", "photos", "length", "carmodel","miles", "yeargroup", "ding", "dent", "scratch", "problem", "rust", "condition")]
newdata3 = newdata3[!is.na(newdata3$biddy1),]
newdata3 = newdata3[!is.na(newdata3$photos),]
newdata3 = newdata3[-which(newdata3$photos==-1),]
table(newdata3$carmodel)
## most common: Ford Mustang
dataFordMustang = which(newdata3$carmodel =="Ford 39")
dataFordMustang = newdata3[dataFordMustang, ]
```

## Recommendation for the auction format
```{r}
library(data.table)
library(ggplot2)
## Buy it now
AverageRevene = data.table(dataFordMustang[-test_ind,])[,.("AverageRevene" = mean(biddy1)),by=c("buyitnow")]
newdatatr = merge(dataFordMustang[-test_ind,],AverageRevene,by=c("buyitnow"))

d = data.frame(newdatatr$buyitnow,newdatatr$AverageRevene)
colnames(d) = c("buyitnow","revenue")
ggplot(d,aes(x=buyitnow,y=newdatatr$biddy1)) + geom_point() 
ggplot(d,aes(x=buyitnow,y=newdatatr$AverageRevene)) + geom_point() 

## Length of time
AverageRevene = data.table(dataFordMustang[-test_ind,])[,.("AverageRevene" = mean(biddy1)),by=c("length")]
newdatatr = merge(dataFordMustang[-test_ind,],AverageRevene,by=c("length"))

d = data.frame(newdatatr$length,newdatatr$AverageRevene)
colnames(d) = c("length","revenue")
ggplot(d,aes(x=length,y=newdatatr$biddy1)) + geom_point() 
ggplot(d,aes(x=length,y=newdatatr$AverageRevene)) + geom_point() 

## Photos
AverageRevene = data.table(dataFordMustang[-test_ind,])[,.("AverageRevene" = mean(biddy1)),by=c("photos")]
newdatatr = merge(dataFordMustang[-test_ind,],AverageRevene,by=c("photos"))

d = data.frame(newdatatr$photos,newdatatr$AverageRevene)
colnames(d) = c("photos","revenue")
ggplot(d,aes(x=photos,y=newdatatr$biddy1)) + geom_point() 
ggplot(d,aes(x=photos,y=newdatatr$AverageRevene)) + geom_point() 

## text
AverageRevene = data.table(dataFordMustang[-test_ind,])[,.("AverageRevene" = mean(biddy1)),by=c("text")]
newdatatr = merge(dataFordMustang[-test_ind,],AverageRevene,by=c("text"))

d = data.frame(newdatatr$text,newdatatr$AverageRevene)
colnames(d) = c("text","revenue")
ggplot(d,aes(x=text,y=newdatatr$biddy1)) + geom_point() 
ggplot(d,aes(x=text,y=newdatatr$AverageRevene)) + geom_point() 

## text less than 5000
datasmalltext = which(newdatatr$text <= 5000)
datasmalltext = newdatatr[datasmalltext, ]
d = data.frame(datasmalltext$text,datasmalltext$AverageRevene)
colnames(d) = c("text","revenue")
ggplot(d,aes(x=text,y=datasmalltext$biddy1)) + geom_point() 
ggplot(d,aes(x=text,y=datasmalltext$AverageRevene)) + geom_point() 

```

